---
title: "Quant_com"
format: 
  pdf:
    include-in-header:
      text: |
        % tables
        \usepackage[l3]{csvsimple}
        \usepackage{nicematrix}
        \usepackage{multirow} % merge rows / columns
        \usepackage{booktabs}
        
        % right aligned columns in nicematrix
        \newcolumntype{Y}{>{\raggedleft\arraybackslash}X}
        
        % Captions and labels (Makes our Caption labels Grey and uppercase :D)
        \usepackage[singlelinecheck=off, font=small]{caption}
        \DeclareCaptionLabelFormat{AnimEco}{\textbf{\color{darkgray!75}\MakeUppercase{#1 #2}}}
        \captionsetup{labelformat=AnimEco,labelsep=quad}
        
        % equation labels
        \usepackage{mathtools,amssymb,amsthm}
        \newtagform{Eq}{(Eq. }{)}
        \usetagform{Eq}
editor: visual
csl: apa.csl
bibliography: Quant_Com_Group.bib
---

## Quantitative Community Ecology in R

Test for Zotero Group Bib: @smilauer2014

[@smilauer2014]

... sweet, works so far

## Running Code

When you click the **Render** button a document will be generated that includes both content and the output of embedded code. You can embed code like this:

```{r}
1 + 1
```

You can add options to executable code like this

```{r}
#| echo: false
2 * 2
```

The `echo: false` option disables the printing of code (only output is displayed).
